H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability

### 2018-12-12 slides-agu/presentation.tex
Try to sketch out some text

% Package List
\usepackage{
  array,                              % for custom table widths
  appendixnumberbeamer,               % don't count appendix slides in progress bar
	booktabs,                           % for better (alternative?) tables
  natbib,                             % references!
	physics,                            % for better notation
  siunitx,                            % for SI notation
  appendixnumberbeamer,               % don't number slides / sections in appendix
}

@@

\begin{frame}{Motivating Example \citep{CityofNewYork:2013uh}}
  \begin{columns}[T]
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\columnwidth]{three-barriers.png}
        \caption{
          Large, permanent project would lock in $\approx \$25 \text{billion}$ for fixed protection.
        }
      \end{figure}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\columnwidth]{flood-concept.png}
        \caption{
          A sequenced portfolio of smaller investments may be more flexible and adaptive.
        }
      \end{figure}
    \end{column}
  \end{columns}
  \begin{alertblock}{Scheduling and sequencing:}
    \alert{If} and \alert{when} to build the permanent project?
  \end{alertblock}
\end{frame}

\section{Underlying Ideas}

@@

\begin{frame}{Idea 2: Hydroclimate Systems Vary on Many Scales}
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth]{observed-lfv.pdf}
    \caption{
      (a) \SI{500}{year} reconstruction of summer rainfall over Arizona from LBDA \citep{Cook:2010bz}.
      (b) A \SI{100}{year} record of annual-maximum streamflows for the American River at Folsom.
      (c),(d): wavelet global (average) spectra.
    }\label{fig:observed-lfv}
  \end{figure}
\end{frame}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How well can one identify and predict risk}
     associated with cyclical and secular climate signals over a finite design life ($M$),  given limited information (\eg, an $N$-year record).
  \end{alertblock}
  \pause
  In particular, we consider:
  \begin{itemize}
    \item the specific roles of $M$ and $N$;
    \pause
    \item estimation strategy (few processes/parameters $\Rightarrow$ many processes/parameters)
    \pause
    \item the form of the underlying climate signal.
  \end{itemize}
  \pause
  Use parsimonious representation of key processes.
\end{frame}

\begin{frame}{Breathless Overview of Methods}
  \begin{columns}[T]
    \begin{column}{0.475\textwidth}
      We will consider:
      \begin{itemize}
        \item 3 scenarios:
        \begin{itemize}
          \item \gls{lfv} only
          \item linear trend only
          \item trend + \gls{lfv}
        \end{itemize}
        \item 3 fitting models:
        \begin{itemize}
          \item stationary
          \item trend
          \item \gls{hmm}
        \end{itemize}
        \item Many values of $\qty{M, N}$
      \end{itemize}
    \end{column}
    \pause
    \begin{column}{0.475\textwidth}
      \begin{figure}
        \caption{Over- or under-estimating uncertainty leads to biased estimates of $p(X > X^*)$ even if estimate of $X$ is unbiased}
        \includegraphics[width=\textwidth]{Example-NINO3-M100-N50-LN2.jpg}
      \end{figure}
      For each combination, use \num{1000} synthetic streamflow sequences to evaluate the expected bias and variance of $p(X > X^*)$
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Summary}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      Assertions:
      \begin{enumerate}
        \item Investment evaluation depends on climate condition over finite planning period
        \item Physical hydroclimate systems vary on many scales
        \item Physical drivers of risk depend on planning period
      \end{enumerate}    
    \end{column}
    \begin{column}{0.5\textwidth}
      Implications:
      \begin{itemize}
        \item \emph{Ability} to identify and predict different climate signals depends on information available (\eg, $N$)
        \item \emph{Importance} of identifying and predicting different climate signals depends on degree of extrapolation desired (\ie, $M$)
        \item In general, low risk tolerance and/or short $N$ favor short-$M$ investments relative to long-$M$ ones.
      \end{itemize}    
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{A Shameless Pitch!}
  I'm working on turning these concepts for project \emph{evaluation} into models for \emph{decision-making}.
  Specifically:
  \begin{itemize}
    \item Integrating paleo records, observations, and \glspl{gcm} for climate risk projection
    \item Valuing the ``option'' to build a particular project
    \item Optimizing portfolios of long- and short-term investments
  \end{itemize}
  If you have a working model of your system and are making long/short-term investment choices I'd \alert{love to talk} further!
\end{frame}

@@

\begin{frame}[standout]
  \alert{Thanks for your attention!}\\\vspace{1.5cm}
  \begin{tabular}{rl}
    \faIcon[regular]{twitter},\faIcon[regular]{github} & \href{https://twitter.com/jdossgollin}{@jdossgollin} \\
    \faIcon[regular]{envelope} & \href{mailto:james.doss-gollin@columbia.edu}{james.doss-gollin@columbia.edu}\\
    \faIcon[regular]{paperclip} & \url{www.jamesdossgollin.me}
  \end{tabular}
\end{frame}

>>>>

% Package List
\usepackage{
  array,                              % for custom table widths
  appendixnumberbeamer,               % don't count appendix slides in progress bar
  booktabs,                           % for better (alternative?) tables
  natbib,                             % references!
	physics,                            % for better notation
  siunitx,                            % for SI notation
}

@@

\begin{frame}{Motivating Example}
  What to do after Sandy? \citep{CityofNewYork:2013uh}
  \begin{figure}
    \centering
    \includegraphics[height=0.3\textheight]{three-barriers.png}~
    \includegraphics[height=0.3\textheight]{flood-concept.png}
    \caption{
      A large, permanent project would lock in $\approx \$25 \text{billion}$ for fixed protection; a portfolio of smaller investments may be more flexible and adaptive.
    }
  \end{figure}
  \pause
  \begin{alertblock}{Scheduling and sequencing:}
    When (and how) to build a flexible portfolio vs mega-project
  \end{alertblock}
\end{frame}

\begin{frame}{Table of contents}
  \setbeamertemplate{section in toc}[sections numbered]
  \tableofcontents[hideallsubsections]
\end{frame}

\section{Hypotheses}

@@

\begin{frame}{Idea 2: Hydroclimate Systems Vary on Many Scales}
  Inter-annual to multi-decadal variability very important in near future (\ie, for small $M$) \citep{Hodgkins:2017hw}
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.55\textheight,keepaspectratio=true]{observed-lfv.pdf}
    \caption{
      (a) \SI{500}{year} reconstruction of summer rainfall over Arizona from LBDA \citep{Cook:2010bz}.
      (b) A \SI{100}{year} record of annual-maximum streamflows for the American River at Folsom.
      (c),(d): wavelet global (average) spectra.
    }\label{fig:observed-lfv}
  \end{figure}
\end{frame}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How well can one identify and predict risk}
     associated with cyclical and secular climate signals over a finite planning period ($M$),  given limited information (\eg, an $N$-year record).
  \end{alertblock}
  \pause
  \begin{columns}
    \begin{column}{0.5\textwidth}
      In particular, we consider:
      \begin{itemize}
        \item the specific roles of $M$ and $N$;
        \pause
        \item estimation strategy (few processes/parameters $\Rightarrow$ many processes/parameters)
        \pause
        \item the form of the underlying climate signal.
      \end{itemize}
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{Example-NINO3-M100-N50-LN2.jpg}
        \caption{
          What is the bias and spread of $p(X > X^*)$?
          Here, $M=100$ and $N=50$.
          Subsequent results are tested systematically over $J=1000$ sequences.
        }
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Summary}
  \begin{columns}[T]
    \begin{column}{0.5\textwidth}
      Assertions:
      \begin{enumerate}
        \item Investment evaluation depends on climate condition over finite planning period
        \item Physical hydroclimate systems vary on many scales
        \item Physical drivers of risk depend on planning period
      \end{enumerate}    
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      Implications:
      \begin{itemize}
        \pause
        \item \emph{Ability} to identify and predict different climate signals depends on information available (\eg, $N$)
        \pause
        \item \emph{Importance} of identifying and predicting different climate signals depends on degree of extrapolation desired (\ie, $M$)
        \pause
        \item In general, low risk tolerance and/or short $N$ favor short-$M$ investments relative to long-$M$ ones.
      \end{itemize}    
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[standout]
  \alert{Thanks for your attention!}\\
  \vspace{1.5cm}
  Interested in making these ideas more concrete?
  I'd love to collaborate!\\
  \vspace{1.5cm}
  \begin{tabular}{rl}
    \faIcon[regular]{twitter},\faIcon[regular]{github} & \href{https://twitter.com/jdossgollin}{@jdossgollin} \\
    \faIcon[regular]{envelope} & \href{mailto:james.doss-gollin@columbia.edu}{james.doss-gollin@columbia.edu}\\
    \faIcon[regular]{paperclip} & \url{www.jamesdossgollin.me}
  \end{tabular}
\end{frame}
